Data preparation

### 2020-08-19 production/prod_prep-data.rmd
update

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = FALSE,results = "hold")
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

@@

### load packages
```{r}
library(sjPlot)
library(sjmisc) # several functions,ej read_stata
library(descr)
library(memisc)  # codebook
library(psych) # cor2latex
library(corrplot) # graph correlations
library(lavaan)
library(stargazer)
library(semTools)
library(plyr) # count
library(dplyr)
#library(car) # recode
library(ggplot2)
#library(Hmisc)
library(tidyverse)
library(data.table)
library(stringr)
library(countrycode)
library(lme4)
library(texreg)
library(mice)
library(ggrepel) # for scatter labels in sjp.scatter
#library(semPlot)
library(haven)
library(sjlabelled)
library(kableExtra)
library(summarytools)
library(tidyselect)
library(magrittr)
library(semPlot)
#library(Hmisc)
library(knitr)

@@

## General preparation
```{r results='hide'}
load(file = "input/data/original/issp.rda")
#load(url('https://raw.githubusercontent.com/franciscomeneses/bases/master/issp.rda'))

@@

### Check & generate IDs (v4: respondent, v5: country)
### Generate new sequential id individuals by country to merge
      issp2009$id <- sequence(tabulate(issp2009
                                     $v5))
    issp2009$idtem=issp2009$v5*10000  
    issp2009$id=issp2009$idtem + issp2009$id
```

@@

# new names(issp2009)
    redistrib$income_dif= redistrib$v33
    redistrib$unemployed= redistrib$v34
    redistrib$taxes     = redistrib$v36
    redistrib$health    = redistrib$v38
    redistrib$educ      = redistrib$v39

#Delete old variables

    redistrib=redistrib[-c(2:6)]

    stargazer(redistrib[-c(1,2)], type="html")  
```

### Recode NAs
```{r results='asis'}
    redistrib[3:7][redistrib[3:7] > 5] <- NA
   stargazer(redistrib[-c(1,2)], type="html")

@@

### adjust labels NAs
```{r}
     get_labels(redistrib$income_dif)
    redistrib[,3:7] <-sjlabelled::set_na(redistrib[,c("income_dif","unemployed", "taxes", "health", "educ")], na = c(8,9))

### Reverse code for SEM models
```{r}
redistrib[3:7]=6-redistrib[3:7]

@@

```{r cache=TRUE, results='hide'}
cfa_red1 <- '
	# latent variables
	redist =~ income_dif + unemployed + taxes 
	accum  =~ health + educ
	'

	  # generate 5 multiple complete datasets 
		out <- mice(redistrib[3:7], m=5)

```{r include=FALSE}

@@

		# fit model for each complete dataset 
		fit1 <- cfa(cfa_red1, data=D1) 
		fit2 <- cfa(cfa_red1, data=D2) 
		fit3 <- cfa(cfa_red1, data=D3) 
		fit4 <- cfa(cfa_red1, data=D4) 
		fit5 <- cfa(cfa_red1, data=D5)

@@

# compute 'average' across 5 sets of scores: 
		scores <- (p1 + p2 + p3 + p4 + p5)/5

 #Generate factor scores      
   scores_dat=as.data.frame(scores)

# Adaptar base para agregar factor scores (sacar todos NA)  
   redistrib_m=redistrib[rowSums(is.na(redistrib[3:7]))!=5,]

# Merge with factor scores
	  redistrib_sco=cbind(redistrib,scores)

	  # Check
	   stargazer(redistrib_sco[,8:9], type ="text")

	# Save  factor scores
	  save(redistrib_sco, file="input/data/proc/redistrib_sco.rda")
```

@@

```{r results='asis'}
### Select

indepvar= issp2009 %>% dplyr::select(contains("_inc"), "sex","age","degree", "hompop", "v44", "v45", "movstatus"="v46", "v5","id")

### Recode sex

sjPlot::plot_frq(indepvar$sex, title ="Gender before")
indepvar$sex=ifelse(indepvar$sex==1,0,ifelse(indepvar$sex==2,1,NA))  
sjPlot::plot_frq(indepvar$sex, title ="gender after")

### Recode Age

  # Age
sjPlot::plot_frq(indepvar$age, title = "Age before",show.mean = T , show.values = F,show.n = F)

@@

### Recode Education

sjPlot::plot_frq(indepvar$degree, coord.flip = TRUE, title = "Degree before")

  # Recode. Values over 5 are removed

  indepvar$degree[indepvar$degree > 5]=NA

@@

  # Agregar ahora todos en un solo vector
indepvar$income=rowSums(indepvar[1:41],na.rm = TRUE)

indepvar$income[indepvar$income ==0]=NA
indepvar$income[indepvar$income ==1111]=0

@@

### Recode Household income

# Household income

@@

@@

# para usarlas habría que clasificar partidos de esos países

@@

```{r}
#indepvar_graph<-as.data.frame(indepvar[,2:16])

print(dfSummary(indepvar[-c(8)], valid.col = FALSE, graph.magnif = 1),
      max.tbl.height = 300, method = "render")
```

@@

```{r results='hide'}
    # Rename
    getahead=issp2009[,c("v6","v7","v9", "v10","v11","v12",
             "v14","v16", # get ahead
    	  		 "v5","id")]

    getahead$wealthy=getahead$v6
    getahead$pareduc=getahead$v7
    getahead$ambition= getahead$v9
    getahead$hwork=getahead$v10
    getahead$people=getahead$v11
    getahead$polcone=getahead$v12
    getahead$race=getahead$v14
    getahead$gender=getahead$v16

    getahead=getahead[-c(1:8)]

@@

  # adjust labels
    get_labels(getahead$wealthy)
    getahead[ , 3:10][getahead[ , 3:10] >= 8] <- NA
    get_labels(getahead[3:10]) # check

  # Reverse code for SEM models
    getahead[3:10]=6-getahead[3:10]

  # Generate variables with 3 values for getahead mess model categoric
    #names(getahead)
    getahead_temp=subset(getahead[c(2,3:10)])
    #names(getahead_temp)
    getahead_temp[2:9][getahead_temp[2:9] <  4] <- 3
   # freq(getahead_temp$hwork)
    #freq(getahead$hwork)

    colnames(getahead_temp)=paste("c3", colnames(getahead_temp),
    	sep="")
    names(getahead_temp)[names(getahead_temp)=="c3id"] <- "id"
    getahead_temp2=merge(getahead,getahead_temp, by=c("id"))
  	names(getahead_temp2) # ok
  	getahead=getahead_temp2

@@

```{r}
	# Save object
  #  save(getahead, file="../objects/getahead.rda")

@@

```{r}
		#names(issp2009)
	  detearn=issp2009[,c("v47", "v48", "v49", "v50", "v51",
	   	"v52", "v5","id")]
names(detearn)
    detearn$respons 	= detearn$v47
    detearn$yeduc  	  = detearn$v48
    detearn$family    = detearn$v49
    detearn$child     = detearn$v50
    detearn$welljob   = detearn$v51
    detearn$hardjob   = detearn$v52
names(detearn)
    detearn=detearn[-c(1:6)]
names(detearn)
  # recode values 8 9 to NA
    summary(detearn)
  # freq(detearn$respons)
    detearn[3:8][detearn[3:8] > 5] <- NA

@@

  # Out Portugal (no answer in well job item)
    detearn[which(detearn$v5==620),]=NA
  # adjust labels ###PROB PORTUCAL!!!
    get_labels(detearn)
detearn[ , 3:8][detearn[ , 3:8] >= 8] <- NA
    detearn$welljob<-sjlabelled::set_na(detearn$welljob, na =c(0))
        knitr::kable(summary(detearn), "html")
   # freq(detearn$welljob) ## prob portugal
    detearn$welljob[detearn$welljob ==0] = NA
    get_labels(detearn$welljob)
    labels(detearn$welljob)=labels(detearn$respons)### PROB NOT SOLVED

# Reverse code for SEM models
    detearn$respons <- as.numeric(detearn$respons)
    detearn$yeduc <- as.numeric(detearn$yeduc)
    detearn$family <- as.numeric(detearn$family)
    detearn$child <- as.numeric(detearn$child)
    detearn$welljob <- as.numeric(detearn$welljob)
    detearn$hardjob <- as.numeric(detearn$hardjob)

```{r}
    sjPlot::plot_likert(detearn[,3:8],
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", "#2171b5"), # colorbrewer2.org 
                        cat.neutral = 3,
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "Before detearn",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6) # expand axis 130% ))

@@

  sjPlot::plot_likert(detearn[,3:8],
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", "#2171b5"), # colorbrewer2.org 
                      cat.neutral = 3,
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "After detearn",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6) # expand axis 130% ))

@@

```{r}
# 3. MEASURING BELIEFS & PERCEPTIONS ------ -

@@

  # Estimación del modelo c/ unmerit 2do orden
	  cfa_perpref2 <- '
	  # latent variables
	  merit =~ hwork + ambition
	  parent=~ wealthy + pareduc
	  backg=~ race + gender
		network=~ people + polcone
		unmerit=~ parent + backg + network # 2nd order
	  bmerit =~ welljob + hardjob
	  need=~ family + child
	  '
	  fit_perpref2 <- cfa(cfa_perpref2,data=merit_per_pref,
	  	missing = "ML")
#	  summary(fit_perpref2, fit.measures=TRUE,standardized=TRUE)

  # Path model
		  semPaths(fit_perpref2,layout = "tree", rotation = 2,
		  	intercepts = FALSE, style = "lisrel", curvePivot = TRUE,
		  	sizeMan = 3.5, sizeLat = 6)
```

@@

```{r cache=TRUE, results='hide'}

			out <- mice(merit_per_pref[,c(3:10,19:24)], m=5)
```

```{r results='hide'}
		# Multiple imputation (para recuperar missings en scores) - REVIEW THIS, command lavPredict from 2017 should predict with missing values therefore saving from multiple imputation

@@

			# fit model for each complete dataset
			fit1 <- cfa(cfa_perpref2, data=D1)
			fit2 <- cfa(cfa_perpref2, data=D2)
			fit3 <- cfa(cfa_perpref2, data=D3)
			fit4 <- cfa(cfa_perpref2, data=D4)
			fit5 <- cfa(cfa_perpref2, data=D5)

@@

		# compute 'average' across 5 sets of scores:
			scores <- (p1 + p2 + p3 + p4 + p5)/5

	  # Generate factor scores
	    scores_dat=as.data.frame(scores)
	    dim(scores_dat)
	    str(scores_dat)
	    summary(scores)

		# Generate object with factor scores
	    dim(merit_per_pref)
	    dim(scores_dat)
		  merit_per_pref_sco=cbind(merit_per_pref,scores)

	# Save object with factor scores
	#	names(merit_per_pref_sco)
		merit_per_pref_sco=merit_per_pref_sco[,c(1:2,25:31)]
#	  save(merit_per_pref_sco,
#	  	file="./objects/merit_per_pref_sco.rda")

@@

```{r}

indiv<- merge (indepvar, redistrib_sco, by = c("id"))

indiv <- merge (indiv,  merit_per_pref_sco, by = c("id"))
```

@@

agg_lm$v5=agg_lm$j_v5

mer_pref=merge(indiv,agg_lm, by="v5")

 dim(mer_pref)

```{r}
    mer_pref$age_g=mer_pref$age-mer_pref$j_age
    mer_pref$sex_g =mer_pref$sex-mer_pref$j_sex
    mer_pref$univ_g =mer_pref$univ-mer_pref$j_univ
  mer_pref$sstatus_g= mer_pref$sstatus-mer_pref$j_sstatus

    summary(mer_pref$univ_g)
```

@@

# convertir desde formato original list a dataframe

swiid_summary <- swiid %>%  bind_rows() %>%
group_by(country, year) %>%  
summarize_all(funs(mean, sd)) %>%
ungroup() %>% dplyr::rename(.dots=setNames(names(.),
str_replace(names(.), "_mean", ""))) %>%  
dplyr::rename_(.dots=setNames(names(.),str_replace(names(.), "_sd", "_se")))

save(swiid_summary, file = "input/data/proc/swiid_summary.rda")

###  Filter only 2009
```{r}
summary(swiid_summary$.dots...year)

swiid_summary09=subset(swiid_summary, .dots...year==2009)
```

@@

```{r}
# Generate equivalente country code

head(swiid_summary09$.dots...country)
as.numeric(swiid_summary09$country)

@@

# Merge
#indepvar <- merge(swiid_summary09,indepvar,by=c("v5"))

#summary(indepvar$.dots..._1_gini_disp)

@@

		# Extract 2009 data
			qog2009=subset(qog, year==2009)

@@

			load("input/data/proc/indepvar_contries.rda")
			issp_countries=	aggregate(indepvar_contries[c("v5")], 
					list(indepvar_contries$country,indepvar_contries$v5c),mean)

			qog2009[c("ccode","cname")] # check ISO codes
			names(qog2009)[names(qog2009) == 'ccode'] <- 'v5'
			qog2009_c=merge(issp_countries, qog2009, by=c("v5")) 
			dim(qog2009_c)
			colSums(is.na(qog2009_c))

			# Eliminar columnas con máximo 5 NAs
			qog2009_c_na= qog2009_c[ , colSums(is.na(qog2009_c)) < 6]

			qog2009_c_na= qog2009_c_na %>% dplyr::select("v5", "fi_index") %>% as.data.frame()
			#names(qog2009_c_na)

# Merge
```{r}

mer_pref <- merge(mer_pref, qog2009_c_na, by=c("v5"))
```

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = TRUE,results = "hold")
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

@@

### load packages

```{r}
library(sjPlot)
library(sjmisc) # several functions,ej read_stata
library(descr)
library(memisc)  # codebook
library(psych) # cor2latex
library(corrplot) # graph correlations
library(lavaan)
library(stargazer)
library(semTools)
library(plyr) # count
library(dplyr)
#library(car) # recode
library(ggplot2)
#library(Hmisc)
library(tidyverse)
library(data.table)
library(stringr)
library(countrycode)
library(lme4)
library(texreg)
library(mice)
library(ggrepel) # for scatter labels in sjp.scatter
#library(semPlot)
library(haven)
library(sjlabelled)
library(kableExtra)
library(summarytools)
library(tidyselect)
library(magrittr)
library(semPlot)
#library(Hmisc)
library(knitr)

@@

## General preparation

```{r results='hide'}
load(file = "input/data/original/issp.rda")
#load(url('https://raw.githubusercontent.com/franciscomeneses/bases/master/issp.rda'))

@@

### Check & generate IDs (v4: respondent, v5: country)
### Generate new sequential id individuals by country to merge
issp2009$id <- sequence(tabulate(issp2009$v5))
issp2009$idtem=issp2009$v5*10000  
issp2009$id=issp2009$idtem + issp2009$id
```

@@

# new names(issp2009)
redistrib$income_dif = redistrib$v33
redistrib$unemployed = redistrib$v34
redistrib$taxes     = redistrib$v36
redistrib$health    = redistrib$v38
redistrib$educ      = redistrib$v39

#Delete old variables
redistrib = redistrib[-c(2:6)]
stargazer(redistrib[-c(1,2)], type="html")  
```

### Recode NAs

```{r results='asis'}
redistrib[3:7][redistrib[3:7] > 5] <- NA
stargazer(redistrib[-c(1,2)], type="html") 
```

@@

### adjust labels NAs

```{r}
get_labels(redistrib$income_dif)
redistrib[,3:7] <-sjlabelled::set_na(redistrib[,c("income_dif","unemployed", "taxes", "health", "educ")], na = c(8,9))  
```

### Reverse code for SEM models

```{r}
redistrib[3:7]=6-redistrib[3:7]
```

@@

```{r cache=TRUE, results='hide'}
cfa_red1 <- '
	# latent variables
	redist =~ income_dif + unemployed + taxes
	accum  =~ health + educ
	'
```

```{r include=FALSE, cache=TRUE}
# generate 5 multiple complete datasets
out <- mice(redistrib[3:7], m = 5)

@@

# fit model for each complete dataset
fit1 <- cfa(cfa_red1, data = D1)
fit2 <- cfa(cfa_red1, data = D2)
fit3 <- cfa(cfa_red1, data = D3)
fit4 <- cfa(cfa_red1, data = D4)
fit5 <- cfa(cfa_red1, data = D5)

@@

# compute 'average' across 5 sets of scores:
scores <- (p1 + p2 + p3 + p4 + p5) / 5

#Generate factor scores
scores_dat = as.data.frame(scores)

# Adaptar base para agregar factor scores (sacar todos NA)
redistrib_m = redistrib[rowSums(is.na(redistrib[3:7])) != 5, ]

# Merge with factor scores
redistrib_sco = cbind(redistrib, scores)

# Check
stargazer(redistrib_sco[, 8:9], type = "text")

# Save  factor scores
save(redistrib_sco, file = "input/data/proc/redistrib_sco.rda")
```

@@

```{r results='asis'}
### Select
indepvar= issp2009 %>% dplyr::select(contains("_inc"), "sex","age","degree", "hompop", "v44", "v45", "movstatus"="v46", "v5","id")

### Recode sex
sjPlot::plot_frq(indepvar$sex, title ="Gender before")
indepvar$sex=ifelse(indepvar$sex==1,0,ifelse(indepvar$sex==2,1,NA))  
sjPlot::plot_frq(indepvar$sex, title ="gender after")

### Recode Age
  # Age
sjPlot::plot_frq(indepvar$age, title = "Age before",show.mean = T , show.values = F,show.n = F)

@@

### Recode Education
sjPlot::plot_frq(indepvar$degree, coord.flip = TRUE, title = "Degree before")
  # Recode. Values over 5 are removed
indepvar$degree[indepvar$degree > 5]=NA

@@

# Agregar ahora todos en un solo vector
indepvar$income=rowSums(indepvar[1:41],na.rm = TRUE)
indepvar$income[indepvar$income ==0]=NA
indepvar$income[indepvar$income ==1111]=0

@@

### Recode Household income
# Household income

@@

knitr::kable(table(indepvar$movstatus), "html")
```

@@

# para usarlas habría que clasificar partidos de esos países
```

@@

```{r}
#indepvar_graph<-as.data.frame(indepvar[,2:16])
print(dfSummary(indepvar[-c(8)], valid.col = FALSE, graph.magnif = 1),
      max.tbl.height = 300, method = "render")
```

@@

```{r results='hide'}
    # Rename
getahead = issp2009[, c("v6", "v7", "v9", "v10", "v11", "v12",
                        "v14", "v16", # get ahead
                        "v5", "id")]

getahead$wealthy = getahead$v6
getahead$pareduc = getahead$v7
getahead$ambition = getahead$v9
getahead$hwork = getahead$v10
getahead$people = getahead$v11
getahead$polcone = getahead$v12
getahead$race = getahead$v14
getahead$gender = getahead$v16

getahead = getahead[-c(1:8)]

@@

# adjust labels
get_labels(getahead$wealthy)
getahead[, 3:10][getahead[, 3:10] >= 8] <- NA
get_labels(getahead[3:10]) # check

# Reverse code for SEM models
getahead[3:10] = 6 - getahead[3:10]

# Generate variables with 3 values for getahead mess model categoric
#names(getahead)
getahead_temp = subset(getahead[c(2, 3:10)])
#names(getahead_temp)
getahead_temp[2:9][getahead_temp[2:9] <  4] <- 3
# freq(getahead_temp$hwork)
#freq(getahead$hwork)

colnames(getahead_temp) = paste("c3", colnames(getahead_temp),
                                sep = "")
names(getahead_temp)[names(getahead_temp) == "c3id"] <- "id"
getahead_temp2 = merge(getahead, getahead_temp, by = c("id"))
names(getahead_temp2) # ok
getahead = getahead_temp2
```

@@

```{r}
# Save object
#  save(getahead, file="../objects/getahead.rda")
```

@@

```{r}
#names(issp2009)
detearn = issp2009[, c("v47", "v48", "v49", "v50", "v51",
                       "v52", "v5", "id")]
names(detearn)
detearn$respons 	= detearn$v47
detearn$yeduc  	  = detearn$v48
detearn$family    = detearn$v49
detearn$child     = detearn$v50
detearn$welljob   = detearn$v51
detearn$hardjob   = detearn$v52
names(detearn)
detearn = detearn[-c(1:6)]
names(detearn)
# recode values 8 9 to NA
summary(detearn)
# freq(detearn$respons)
detearn[3:8][detearn[3:8] > 5] <- NA

@@

# Out Portugal (no answer in well job item)
detearn[which(detearn$v5 == 620), ] = NA
# adjust labels ###PROB PORTUCAL!!!
get_labels(detearn)
detearn[, 3:8][detearn[, 3:8] >= 8] <- NA
detearn$welljob <- sjlabelled::set_na(detearn$welljob, na = c(0))
knitr::kable(summary(detearn), "html")
# freq(detearn$welljob) ## prob portugal
detearn$welljob[detearn$welljob == 0] = NA
get_labels(detearn$welljob)
labels(detearn$welljob) = labels(detearn$respons)### PROB NOT SOLVED

# Reverse code for SEM models
detearn$respons <- as.numeric(detearn$respons)
detearn$yeduc <- as.numeric(detearn$yeduc)
detearn$family <- as.numeric(detearn$family)
detearn$child <- as.numeric(detearn$child)
detearn$welljob <- as.numeric(detearn$welljob)
detearn$hardjob <- as.numeric(detearn$hardjob)
```

```{r}
sjPlot::plot_likert(detearn[, 3:8],
                    geom.colors   = c("#9ecae1", "#6baed6", "#4292c6", "#2171b5"), # colorbrewer2.org
                    cat.neutral = 3,
                    sort.frq      = "neg.asc", # sort descending)
                    title         = "Before detearn",
                    intercept.line.color = "white", # vertical middle
                    expand.grid   = F, # no inner margins in plot
                    show.n        = FALSE, # hide N's in axis labels
                    grid.range    = 1.8,
                    geom.size = 0.6) # expand axis 130% ))

@@

sjPlot::plot_likert(detearn[,3:8],
                    geom.colors   = c("#9ecae1", "#6baed6", "#4292c6", "#2171b5"), # colorbrewer2.org
                    cat.neutral = 3,
                    sort.frq      = "neg.asc", # sort descending)
                    title         = "After detearn",
                    intercept.line.color = "white", # vertical middle
                    expand.grid   = F, # no inner margins in plot
                    show.n        = FALSE, # hide N's in axis labels
                    grid.range    = 1.8,
                    geom.size = 0.6) # expand axis 130% ))

@@

```{r, cache=TRUE}
# 3. MEASURING BELIEFS & PERCEPTIONS ------ -

@@

  # Estimación del modelo c/ unmerit 2do orden
cfa_perpref2 <- '
	  # latent variables
	  merit =~ hwork + ambition
	  parent=~ wealthy + pareduc
	  backg=~ race + gender
		network=~ people + polcone
		unmerit=~ parent + backg + network # 2nd order
	  bmerit =~ welljob + hardjob
	  need=~ family + child
	  '
fit_perpref2 <- cfa(cfa_perpref2, data = merit_per_pref,missing = "ML")
#	  summary(fit_perpref2, fit.measures=TRUE,standardized=TRUE)
  # Path model
		  semPaths(fit_perpref2,layout = "tree", rotation = 2,
		  	intercepts = FALSE, style = "lisrel", curvePivot = TRUE,
		  	sizeMan = 3.5, sizeLat = 6)
```

@@

```{r cache=TRUE, results='hide'}
out <- mice(merit_per_pref[,c(3:10,19:24)], m=5)
```

```{r results='hide', cache=TRUE}
# Multiple imputation (para recuperar missings en scores) - REVIEW THIS, command lavPredict from 2017 should predict with missing values therefore saving from multiple imputation

@@

# fit model for each complete dataset
fit1 <- cfa(cfa_perpref2, data = D1)
fit2 <- cfa(cfa_perpref2, data = D2)
fit3 <- cfa(cfa_perpref2, data = D3)
fit4 <- cfa(cfa_perpref2, data = D4)
fit5 <- cfa(cfa_perpref2, data = D5)

@@

# compute 'average' across 5 sets of scores:
scores <- (p1 + p2 + p3 + p4 + p5) / 5

# Generate factor scores
scores_dat = as.data.frame(scores)
dim(scores_dat)
str(scores_dat)
summary(scores)

# Generate object with factor scores
dim(merit_per_pref)
dim(scores_dat)
merit_per_pref_sco = cbind(merit_per_pref, scores)

# Save object with factor scores
#	names(merit_per_pref_sco)
merit_per_pref_sco = merit_per_pref_sco[, c(1:2, 25:31)]
#	  save(merit_per_pref_sco,
#	  file="./objects/merit_per_pref_sco.rda")

@@

```{r}
indiv<- merge (indepvar, redistrib_sco, by = c("id"))
indiv <- merge (indiv,  merit_per_pref_sco, by = c("id"))
```

@@

agg_lm$v5=agg_lm$j_v5	
mer_pref=merge(indiv,agg_lm, by="v5")

dim(mer_pref)
```

```{r}
mer_pref$age_g = mer_pref$age - mer_pref$j_age
mer_pref$sex_g = mer_pref$sex - mer_pref$j_sex
mer_pref$univ_g = mer_pref$univ - mer_pref$j_univ
mer_pref$sstatus_g = mer_pref$sstatus - mer_pref$j_sstatus
summary(mer_pref$univ_g)
```

@@

# convertir desde formato original list a dataframe
swiid_summary <- swiid %>%  bind_rows() %>%
group_by(country, year) %>%  
summarize_all(funs(mean, sd)) %>%
ungroup() %>% dplyr::rename(.dots=setNames(names(.),
str_replace(names(.), "_mean", ""))) %>%  
dplyr::rename_(.dots=setNames(names(.),str_replace(names(.), "_sd", "_se")))

save(swiid_summary, file = "input/data/proc/swiid_summary.rda")
```

###  Filter only 2009
```{r}
summary(swiid_summary$.dots...year)
swiid_summary09=subset(swiid_summary, .dots...year==2009)
```

@@

```{r}
# Generate equivalente country code
head(swiid_summary09$.dots...country)
as.numeric(swiid_summary09$country)

@@

# Merge
#indepvar <- merge(swiid_summary09,indepvar,by=c("v5"))
#summary(indepvar$.dots..._1_gini_disp)
```

@@

# Extract 2009 data
qog2009 = subset(qog, year == 2009)

@@

load("input/data/proc/indepvar_contries.rda")
issp_countries =	aggregate(indepvar_contries[c("v5")],
                           list(indepvar_contries$country, indepvar_contries$v5c),
                           mean)

qog2009[c("ccode", "cname")] # check ISO codes
names(qog2009)[names(qog2009) == 'ccode'] <- 'v5'
qog2009_c = merge(issp_countries, qog2009, by = c("v5"))
dim(qog2009_c)
colSums(is.na(qog2009_c))

# Eliminar columnas con máximo 5 NAs
qog2009_c_na = qog2009_c[, colSums(is.na(qog2009_c)) < 6]

qog2009_c_na = qog2009_c_na %>% dplyr::select("v5", "fi_index") %>% as.data.frame()
#names(qog2009_c_na)
```

# Merge

```{r}
mer_pref <- merge(mer_pref, qog2009_c_na, by=c("v5"))
```
